ITC Postdoctoral Fellowship Research Proposal: \\ The Role of Disk Volatile Chemistry and Dynamics in Shaping the Compositions of Nascent Planets

### 2015-11-11 Postdoc Applications/AnaMariaPisoResume.tex
update

\begin{list2}
\item[] {\bf C/O and Snowline Locations in Protoplanetary Disks: The Effect of Radial Drift and Viscous Gas Accretion} \\
Extreme Solar Systems III, Waikoloa, HI, December 2015 \\
Poster \\
\end{list2}

>>>>

\begin{list2}
\item[] {\bf C/O and Snowline Locations in Protoplanetary Disks: The Effect of Radial Drift and Viscous Gas Accretion} \\
Extreme Solar Systems III, Waikoloa Village, HI, December 2015 \\
Poster \\
\end{list2}

\begin{list2}
\item[] {\bf Giant Planet Formation and Snowlines in Protoplanetary Disks} \\
University of Michigan Astronomy Lunch Talk, Ann Arbor, MI, November 2015 \\
Seminar speaker \\
\end{list2}
